Enhanced Material Point Method to face dynamic problems:\thanks{Funding: This study was funded by Agustín de Betancourt Foundation (grant number 262390106114).}

### 2020-03-15 ListaFiguras.tex
Cambios 14-3-2020

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \input{Figures/Dyka_bar.tex}}
  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
  \label{fig:Dyka_Bar}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
  }
  \caption{Velocity evolution in the bar left side. This picture
    shows a comparison of both time integration algorithms,
    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
  \label{fig:Velocity-Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Stress_FE_vs_PCE_CFL_05}
  }
  \caption{Stress evolution in the bar left side. This picture
    shows a comparison of both time integration algorithms,
    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
  \label{fig:Stress-Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Velocity-Dyka-LME-gamma-comparative}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Velocity-Dyka-MPM-vs-OTM}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_Q4_vs_uGIMP_LME_Dyka}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Velocity-Dyka-Q4-uGIMP-LME}
\end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \input{Figures/Block.tex}}
  \caption{Geometrical description of a soil block }.}
  \label{fig:block}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
  }
  \caption{Comparative of the vertical displacement evolution in a
    point located in the free surface employing different
    interpolation schemes and numerical techniques.} 
  \label{fig:vertical-displacement-block}
\end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_right_Velocity.png}
  }
  \caption[Velocities values in the right side of the Dyka
  bar]{Analytical solution for the velocity in the right side of the Dyka bar.}
  \label{fig:vel_analytics_dyka}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_left_Stress.png}
  }
  \caption[Stress values in the last quarter side of the Dyka
  bar]{Analytical solution for the stress in the last quarter of the Dyka bar.}
  \label{fig:stress_analytics_dyka}
\end{figure}

>>>>

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{
    \input{Figures/Dyka_bar.tex}}
  \caption{Geometrical description of the Dyka \cite{Dyka1995} bar.}
  \label{fig:Dyka_Bar}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_FE_vs_PCE_CFL_05}
  }
  \caption{Velocity evolution in the bar left side. This picture
    shows a comparison between both time integration algorithms,
    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
  \label{fig:Velocity-Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Stress_FE_vs_PCE_CFL_05}
  }
  \caption{Stress evolution in the bar left side. This picture
    shows a comparison between both time integration algorithms,
    the Forward-Euler (FE) and the Predictor-Corrector explicit (PCE).}
  \label{fig:Stress-Dyka-PCE-FE}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_LME_gamma_comparative}
  }
  \caption{Velocity evolution in the bar left side. This picture
    shows how variation of $\gammma$ affect in a simulation
    with no grid grossing.}
  \label{fig:Velocity-Dyka-LME-gamma-comparative}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity_MPM_vs_OTM_Dyka}
  }
  \caption{Velocity evolution in the bar left side. This picture
    shows a comparison between the optimal transportation mesh-free
    (OTM) method and the material point method (MPM) using the same
    time integration scheme and and spacial discretization.}
  \label{fig:Velocity-Dyka-MPM-vs-OTM}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.85\hsize}{!}{    \includegraphics[width=\textwidth]{./Figures/Velocity_Q4_vs_uGIMP_LME_Dyka}
  }
  \caption{Velocity evolution in the bar left side. This picture
    shows a comparison between the three different interpolation
    techniques using the explicit predictor corrector to perform the
    simulations.}
  \label{fig:Velocity-Dyka-Q4-uGIMP-LME}
\end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{0.8\hsize}{!}{
    \input{Figures/Block.tex}}
  \caption{Initial setting of material points and grid nodes in the
    soil block. The soil is fixed horizontally along the vertical
    walls and vertically along the bottom. The units of the axis are meters.}}
  \label{fig:block}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.9\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_Comparative}
  }
  \caption{Comparative of the vertical displacement evolution in a
    point located in the free surface employing different
    interpolation schemes and numerical techniques.} 
  \label{fig:vertical-displacement-block}
\end{figure}

@@

\begin{figure}\sidecaption
  \centering
  \resizebox{0.9\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_right_Velocity.png}
  }
  \caption[Velocities values in the right side of the Dyka
  bar]{Analytical solution for the velocity in the right side of the Dyka bar.}
  \label{fig:vel_analytics_dyka}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{0.9\hsize}{!}{
    \includegraphics[width=\columnwidth]{Figures/1D_left_Stress.png}
  }
  \caption[Stress values in the last quarter side of the Dyka
  bar]{Analytical solution for the stress in the last quarter of the Dyka bar.}
  \label{fig:stress_analytics_dyka}
\end{figure}
